---
title: "Day 9 Practice"
output: html_document
---

1. Use the following data:

```{r}

myiris <- iris
set.seed(42)
for(col in 1:4) {
  myiris[sample(nrow(myiris), 20, replace = FALSE), col] <- NA
}

```

2. Write a function that will:
  - take a vector of numbers as input
  - return the log of the largest non-NA value
  - Try this out on a vector that you make up

```{r}

Maximum.Value <- function(x) {
  library(dplyr)
  y <- log(x)
  y.NoNA <- y[!is.na(y)]
  Output <- max(y.NoNA)
  Output  
}

x.Result <- Maximum.Value(1:10)
x.Result

```

3. Run this function over rows of the data from #1

```{r}

library(dplyr)
measurement <- log(myiris$Sepal.Length)
measurement.NoNA <- measurement[!is.na(measurement)]
Output <- max(measurement.NoNA)
Output





Maximum.Value <- function(x) {
  library(dplyr)
  y <- log(x)
  y.NoNA <- y[!is.na(y)]
  Output <- max(y.NoNA)
  Output  
}

Sepal.Length.Result <- Maximum.Value(myiris$Sepal.Length)
Sepal.Length.Result

Sepal.Width.Result <- Maximum.Value(myiris$Sepal.Width)
Sepal.Width.Result

Petal.Length.Result <- Maximum.Value(myiris$Petal.Length)
Petal.Length.Result

Petal.Width.Result <- Maximum.Value(myiris$Petal.Width)
Petal.Width.Result

All.Results <- cbind(Sepal.Length.Result, Sepal.Width.Result, Petal.Length.Result, Petal.Width.Result)
All.Results

```

4. Write a function that will get the standard error of a vector of numbers. Use that function to get a standard error for each measure for each Species in the data from #1 (ignoring NAs)

```{r}

Standard.Error <- function(x, ignore.na = TRUE) { 
  if(!ignore.na) {
    Output <- sd(x)/sqrt(length(x)) 
  } else {
    Numerator <- sd(x, na.rm = TRUE)
    Denominator <- sqrt(length(which(!is.na(x))))
    Output <- Numerator/Denominator
  }
  Output
}

Sepal.Length.Result <- Standard.Error(myiris$Sepal.Length)
Sepal.Length.Result

Sepal.Width.Result <- Standard.Error(myiris$Sepal.Width)
Sepal.Width.Result

Petal.Length.Result <- Standard.Error(myiris$Petal.Length)
Petal.Length.Result

Petal.Width.Result <- Standard.Error(myiris$Petal.Width)
Petal.Width.Result

All.Results <- cbind(Sepal.Length.Result, Sepal.Width.Result, Petal.Length.Result, Petal.Width.Result)
All.Results

```