---
title: "Day 3 Homework"
output: html_document
---

The goal of this homework is to get practice with manipulating data.

1. Make both a "wide" and a "long" version of your data

```{r}

library(reshape2)

AlisonTsengData <- read.csv("/Users/Ian/Documents/R_Class/Day_2/Data.csv")

head(AlisonTsengData)

AlisonTsengData$Unique <- c(1:1307) 
AlisonTsengData

head(AlisonTsengData)
AlisonTsengData.Wide <- dcast(AlisonTsengData, ENGLISH_WORD + Unique ~ AMBIGUITY + AMBIGUITY_SOURCE, value.var = "NUMBER_OF_TRANSLATIONS")
AlisonTsengData.Wide

head(AlisonTsengData.Wide)
AlisonTsengData.Long <- melt(AlisonTsengData.Wide, id.vars = c("ENGLISH_WORD", "Unique"))
AlisonTsengData.Long

```

2. Transform a variable

```{r}

head(AlisonTsengData)
AlisonTsengData$Transformation <- AlisonTsengData$NUMBER_OF_TRANSLATIONS * 10
head(AlisonTsengData)

```
3. Recode a factor

```{r}

levels(AlisonTsengData$AMBIGUITY_SOURCE)
levels(AlisonTsengData$AMBIGUITY_SOURCE) <- c("Unambiguous", "Form", "FM", "Meaning")
summary(AlisonTsengData)

```

4. Add a new factor, where the levels are conditional on the values of some other variable. E.g., a factor of "high", "medium", and "low" based on thresholds for another variable.

```{r}

summary(AlisonTsengData)
start <- AlisonTsengData[AlisonTsengData$NUMBER < 281, ]
nrow(start)
start$Order <- "Start"
levels(start$Order) <- "Start"
head(start)

end <- AlisonTsengData[AlisonTsengData$NUMBER >= 281, ]
nrow(end)
end$Order <- "End"
levels(end$Order) <- "End"
head(end)

AlisonTsengData.NewFactor <- rbind(start, end)
summary(AlisonTsengData.NewFactor)

```

5. Reorder the levels of this new factor

```{r}

levels(AlisonTsengData.NewFactor$Order)
AlisonTsengData.NewFactor$Order <- relevel(AlisonTsengData.NewFactor$Order, "End")
levels(AlisonTsengData.NewFactor$Order)

```

6. Choose a factor that could be re-coded as multiple dimensions (recall the sepal/petal vs. length/width breakdown). If you don't have one, try to create one.  Now create two (or more) new factors that represent these dimensions.

```{r}

head(AlisonTsengData.NewFactor)
levels(AlisonTsengData.NewFactor$AMBIGUITY_SOURCE)
levels(AlisonTsengData.NewFactor$AMBIGUITY_SOURCE) <- c("Unambiguous", "Ambiguous", "Ambiguous", "Ambiguous")
levels(AlisonTsengData.NewFactor$AMBIGUITY_SOURCE)
head(AlisonTsengData.NewFactor)
AlisonTsengData.NewFactor2 <- dcast(AlisonTsengData.NewFactor, ENGLISH_WORD + Order + Unique ~ AMBIGUITY_SOURCE, value.var = "NUMBER_OF_TRANSLATIONS")
head(AlisonTsengData.NewFactor2)

```

7. Using `dcast`, aggregate some variable into "cell means" of some kind.

```{r}

AlisonTsengData.Aggregate <- dcast(AlisonTsengData.NewFactor, Order ~ ., value.var = "NUMBER_OF_TRANSLATIONS", fun.aggregate = mean, na.rm = TRUE)
AlisonTsengData.Aggregate

```

8.  Save all of the above in a well-documented R Markdown document.  Email me the .Rmd file (and if you use different or updated data from Day 2 Homework, send that to me, too).
