---
title: "Day 8 Homework"
output: html_document
---

1. Try to recreate the results of Homework 6 (or your intended results) using the `dplyr` functions.

```{r}

library(dplyr)

AlisonTsengData <- read.csv("/Users/Ian/Documents/R_Class/MyHomework/Day_2/Data_Alison_Tseng.csv")
head(AlisonTsengData)

AlisonTsengData %>%
  filter(!is.na(AlisonTsengData$AOA + AlisonTsengData$KFFRQ + AlisonTsengData$NPHN + AlisonTsengData$logstl)) %>%
  group_by(AMBIGUITY_SOURCE) %>%
  summarize(mean.CNC = mean(CNC))

```

2. Find another kind of analysis/transformation/summary stat that you want to apply across multiple groups in your data. Use the functions from `reshape2` and `dplyr` to get these results.

```{r}

library(dplyr)
library(reshape2)

AlisonTsengData <- read.csv("/Users/Ian/Documents/R_Class/MyHomework/Day_2/Data_Alison_Tseng.csv")
head(AlisonTsengData)

AlisonTsengData.subset <- select(AlisonTsengData, ENGLISH_WORD:FAM, IMG:NSYL)
summary(AlisonTsengData.subset)

AlisonTsengData.melt <- melt(AlisonTsengData.subset, id.vars = c("ENGLISH_WORD", "NUMBER_OF_TRANSLATIONS", "AMBIGUITY", "AMBIGUITY_SOURCE"), variable.name = "CHARACTERISTICS", value.name = "MEASUREMENT")
head(AlisonTsengData.melt)

AlisonTsengData.melt %>%
  filter(!is.na(AlisonTsengData.melt$MEASUREMENT)) %>%
  group_by(CHARACTERISTICS, AMBIGUITY_SOURCE) %>%
  summarize(mean = mean(as.numeric(MEASUREMENT)))

```

3. For more practice, try another example of something like #2 (find another stat or grouping or something).

```{r}

library(dplyr)
library(reshape2)

AlisonTsengData <- read.csv("/Users/Ian/Documents/R_Class/MyHomework/Day_2/Data_Alison_Tseng.csv")
head(AlisonTsengData)

AlisonTsengData.subset <- select(AlisonTsengData, ENGLISH_WORD:FAM, IMG:NSYL)
summary(AlisonTsengData.subset)

AlisonTsengData.melt <- melt(AlisonTsengData.subset, id.vars = c("ENGLISH_WORD", "NUMBER_OF_TRANSLATIONS", "AMBIGUITY", "AMBIGUITY_SOURCE"), variable.name = "CHARACTERISTICS", value.name = "MEASUREMENT")
head(AlisonTsengData.melt)

AlisonTsengData.melt %>%
  filter(!is.na(AlisonTsengData.melt$MEASUREMENT)) %>%
  group_by(CHARACTERISTICS, AMBIGUITY) %>%
  summarize(mean = mean(as.numeric(MEASUREMENT)))

```

4. Do yet another case of #2 above, but this time throw in a transformation, too.

```{r}

library(dplyr)
library(reshape2)

AlisonTsengData <- read.csv("/Users/Ian/Documents/R_Class/MyHomework/Day_2/Data_Alison_Tseng.csv")
head(AlisonTsengData)

AlisonTsengData.subset <- select(AlisonTsengData, ENGLISH_WORD:FAM, IMG:NSYL)
summary(AlisonTsengData.subset)

AlisonTsengData.melt <- melt(AlisonTsengData.subset, id.vars = c("ENGLISH_WORD", "NUMBER_OF_TRANSLATIONS", "AMBIGUITY", "AMBIGUITY_SOURCE"), variable.name = "CHARACTERISTICS", value.name = "MEASUREMENT")
head(AlisonTsengData.melt)

AlisonTsengData.melt %>%
  filter(!is.na(AlisonTsengData.melt$MEASUREMENT)) %>%
  group_by(CHARACTERISTICS, NUMBER_OF_TRANSLATIONS) %>%
  summarize(mean = mean(as.numeric(MEASUREMENT)))

```