---
title: "Day 8 Practice"
output: html_document
---

1. Start with this data:

```{r}

library(dplyr)
library(reshape2)

minpair <- read.csv("/Users/Ian/Documents/R_Class/r_programming_bsos/scottdata/CognitionPaperFinalData.csv")

```

2. Get the means of `WithinMinPairs` for each level of `Corpus`

```{r}

minpair %>%
  group_by(Corpus) %>%
  summarize(mean.WithinMinPairs = mean(WithinMinPairs))

```

3. Get cell means of `WithinMinPairs` by `Corpus` and `Merged`

```{r}

minpair %>%
  group_by(Corpus, Merged) %>%
  summarize(mean.WithinMinPairs = mean(WithinMinPairs))

```

4. Melt down the last four columns, which are all frequency measures.  Get the min, max, and mean log values for all of these measures, by Corpus and Merged.
  - HINT: melt down the frequency columns first

```{r}

head(minpair)

minpair.melt <- melt(minpair, measure.vars = c("HiSegTok", "LoSegTok", "HiSegType", "LoSegType"), variable.name = "MeasureName", value.name = "Measure")

head(minpair.melt)

minpair.melt %>%
  group_by(MeasureName, Corpus, Merged) %>%
  summarize(min.Measure = min(Measure), max.Measure = max(Measure), logmean.Measure = log(mean(Measure)))

```

5. Do the same as 4, but only where HiSegTok is greater than the median value for each Corpus.

```{r}

step1 <- minpair %>%
  group_by(Corpus) %>%
  summarize(median.HiSegTok = median(HiSegTok))
step1

minpair.merged <- merge(step1, minpair)
head(minpair.merged)

minpair.filtered <- filter(minpair.merged, HiSegTok > median.HiSegTok)
head(minpair.filtered)

minpair.melt <- melt(minpair.filtered, measure.vars = c("HiSegTok", "LoSegTok", "HiSegType", "LoSegType"), variable.name = "MeasureName", value.name = "Measure")
head(minpair.melt)

minpair.melt %>%
  group_by(MeasureName, Corpus, Merged) %>%
  summarize(min.Measure = min(Measure), max.Measure = max(Measure), logmean.Measure = log(mean(Measure)))

```